A generalized definition of multidimensional item response theory parameters

### 2023-03-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Adapts draft to work with the last changes merged from the main branch

Multidimensional item response theory (MIRT) models have been widely used since
their inception.<!--# Ref. needed? -->
The so called *Multidimensional 2-Parameter Logistic*
[M2PL, @mckinley_extension_1983] model is among the most important
and widely used ones.
This is partly due to its close relationship to the common factor model
[@mcdonald_test_1999], but also to the formal tractability of its formulation.<!--# Ref. needed? -->
It consists of a generalization of the 2-parameter logistic model
[@birnbaum_latent_1968] to more than one latent trait
[@mckinley_extension_1983].
Its usefulness lies in describing the variability of the population when
the correct response does not depend on a single trait;
more specifically, when a deficit in a certain trait
and a surplus in another one cancel out their effects. Because of this property,
it is sometimes referred to as a *compensatory* model.

@reckase_difficulty_1985 argues for a need to take dimensionality into account
when characterizing the statistical properties of multidimensional items.
As such, he outlines a general procedure for determining their difficulty.
Following this procedure, he also derives
a *multidimensional difficulty* parameter (MID) for `r MODEL_ACRONYM` items.
This parameter consists of two parts:
The first one is a scalar value representing the distance from
the origin of the multidimensional latent space to
the maximally discriminating locus of the item.
The second one, the direction of the vector from the origin to that same locus.
Following a similar rationale, @reckase_discriminating_1991 derive a
*multidimensional discrimination* (`r MDISC_PARAM`) parameter definition
for that model.

@@

According to the M2PL model, the probability of a positive response to item
$`r ITEM_INDEX`$ is

>>>>

Multidimensional item response theory (MIRT) models have been widely used since
their inception.<!--# Ref. needed? -->
The so called *Multidimensional 2-Parameter Logistic*
[`r MODEL_ACRONYM`, @mckinley_extension_1983] model is among the most important
and widely used ones.
This is partly due to its close relationship to the common factor model
[@mcdonald_test_1999], but also to the formal tractability of its formulation.<!--# Ref. needed? -->
It consists of a generalization of the 2-parameter logistic model
[@birnbaum_latent_1968] to more than one latent trait
[@mckinley_extension_1983].
Its usefulness lies in describing the variability of the population when
the correct response does not depend on a single trait;
more specifically, when a deficit in a certain trait
and a surplus in another one cancel out their effects. Because of this property,
it is sometimes referred to as a *compensatory* model.

@reckase_difficulty_1985 argues for a need to take dimensionality into account
when characterizing the statistical properties of multidimensional items.
As such, he outlines a general procedure for determining their difficulty.
Following this procedure, he also derives
a *multidimensional difficulty* parameter (MID) for `r MODEL_ACRONYM` items.
This parameter consists of two parts:
The first one is a scalar value representing the distance from
the origin of the multidimensional latent space to
the maximally discriminating locus of the item.
The second one, the direction of the vector from the origin to that same locus.
Following a similar rationale, @reckase_discriminating_1991 derive a
*multidimensional discrimination* (`r MDISC_SYM`) parameter definition
for that model.

@@

According to the `r MODEL_ACRONYM` model, the probability of
a positive response to item $`r ITEM_INDEX`$ is
